Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-17 Grassmannian_cells.tex

  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(U,V)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
  \end{itemize}
  By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or non fibres over $B_l\times C_k$ are empty.
  This shows the compatibility with the image.
  If the fiber is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
  Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.

>>>>

  Proposition~\ref{fibers} shows that the fiber of $\Psi_{\tbff,\tbfg}$ over $(U,V)\in B_\ell\times C_k$ is empty exactly when $\tbfg=\udim\tilde P_{m+1}^I$ and one of the following conditions is satisfied
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$.
  \end{itemize}
By induction, the compatibility condition ($\dagger$) is true for $\pi_{m,j}^\bfJ$  which shows that either all or none of the fibers over $B_l\times C_k$ are empty. This shows the compatibility with the image. If the fiber is not empty, Theorem \ref{vb} gives that we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$  of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$. Altogether this establishes a cell decomposition of $\Gr_{\tbfe}^{\tilde Q}(\tilde P_{m+1}^J)$.
